% LaTeX resume using resume.cls
\documentclass[line,margin]{resume}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font

\begin{document}

\name{H\'{e}lder Tavares da Silva}
% \address used twice to have two lines of address
\address{Currently living in Porto, Portugal}
\address{helder.tavares.silva@gmail.com or +351917534732}

\begin{resume}

\section{OBJECTIVE} Web Software Development, mainly back-end (C\#, Python, Ruby and PHP).

\section{SKILLS}
    {\sl\bf Languages \& Software:}
        C\# Ruby, Rails, Python, Django, JavaScript, PHP, MySQL, PostgreSQL, AMQP, HTML and CSS.\\
        Familiar with various development software methods, Scrum, Extreme Programming and Kanban.\\
        Experience in version control systems, centralized (Subversion) and distributed (Git).\\
        Good Linux (Debian based) system administrator knowledge.

    {\sl\bf Others:}
        Good English writing and reading capabilities.\\
        European Class B driving license.

\section{EXPERIENCE}
    {\sl\bf Senior Software developer, Abyssal} \hfill 06/06/2014 to now
    \begin{itemize}
		\item Currently working in Abyssal Cloud, a web application developed using .NET Core and Angular.io. This product aim is to integrate all the other Abyssal applications in an online platform that will help manage assets and operations of oil \& gas companies.
        \item Worked in a DVR feature of the C\# desktop application Abyssal Offshore. This feature helped companies record their deep sea operations.
		\item Developed a key management system in Django to manage licenses for Abyssal products. The previous method involved sending license files to customers and ask them for hardware ids of the machines the software was intended to run.
		\item Abyssal self-hosts its own development and storage tools (Jira, Confluence, BitBucket, TeamCity, Jenkins, FreeNAS, etc.). I'm responsible of maintaining and upgrading those tools.
		\item I’m responsible for all hardware procurement and maintenance for the company (6 servers and 30 desktops). I also supervise the technical side of the company hardware sales division.
    \end{itemize}

    {\sl\bf Senior Software developer, Porto Tech Center} \hfill 02/06/2014 to 03/06/2016
    \begin{itemize}
		\item Worked in the Kaymu project, a business-to-consumer and consumer-to-consumer marketplace in PHP, I was responsible for integrating new payment APIs, social platform authentication systems, and developing the mobile REST API.
		\item Developed and maintained a notifications counter system for the platform users. These counters were previously calculated synchronously on each page request, so we had to redesign the feature using RabbitMQ and asynchronous requests.
		\item Although I'm mostly focused in the back-end, I've also helped develop and fix some front-end parts in JavaScript and SCSS.
    \end{itemize}
    {\sl\bf Senior Software developer, Kentra Technologies Portugal} \hfill 17/11/2012 to 31/01/2014
    \begin{itemize}
        \item Worked on an information system for analyses laboratories. It was completely built from scratch using Ruby on Rails 3.2 and various gems (simple form, drapper, virtus, etc.). Front-end features and layout were developed using SCSS and CoffeeScript. Deploying was made using capistrano. Extensive use of the git flow model. Also worked with sidekiq and resque providing good know how on background jobs.
        \item Built a solution using ASP.NET Web API to provide a more straightforward way to communicate with a DLL that served as a way of interacting with SAGE Next accounting system.
    \end{itemize}

    {\sl\bf Technical Analyst, Deloitte Portugal} \hfill 01/04/2011 to 30/04/2012
    \begin{itemize}
        \item Worked on the renovation of the entire application framework of a bank. I was part of the integration initiative ensuring automated communication of information received and sent to major payment system.
        \item I developed components using Oracle SOA Suite, database components using Oracle PL/SQL and application components based on Java.
    \end{itemize}

    {\sl\bf Software developer, NDrive Navigation Systems S.A.} \hfill 01/10/2009 to 28/02/2011
     \begin{itemize}
         \item During my master thesis I developed a fully customizable web store that can be easily integrated in existing websites (NDrive's Partner Program). This allowed me to develop my expertise in Django, Python and object-oriented programming.
         \item After presenting my thesis, I was mainly allocated to an in-app purchases and licensing system back-end (Django and PostgreSQL). I implemented critical features (payment system, product dependencies, product updates) and helped improve server performance (50\% less DB queries).
        \item Integrated various in-house heterogeneous systems using message queues (RabbitMQ).
        \item Active role in implementing a build and packaging management system. Allowed me get experience using Django Celery (a distributed tasks server).
        \item Participated in continuous deployment  environment, highly test aware. Every deploy to production (roughly once a day) required peer review and proper automated testing (using unittest and nose).
     \end{itemize}
    {\sl\bf Computer systems designer and analyst, BioStrument S.A.} \hfill 01/09/2007 to 30/09/2009
     \begin{itemize}
         \item Collected requirements, designed, implemented and maintained an information system for sensory analysis laboratories using PHP and MySQL.
         \item I successfully used Doctrine (a PHP ORM) and changed the company's administration opinion about using open-source packages to reduce implementation effort.
     \end{itemize}

\section{EDUCATION}
    {\sl\bf Masters in Informatics and Computing Engineering}\\
    % \sl will be bold italic in New Century Schoolbook (or any postscript font)
    % and just slanted in Computer Modern (default) font
    Faculty of Engineering of the University of Porto, Rua do Dr. Roberto Frias, 4200-464\\
    Ended: 30 September 2010\\
    Final classification 13 in 20. Thesis classification 17 in 20.

\end{resume}
\end{document}
